ABC multi-criteria classification with analytical hierarchy process: how to force consistency of pairwise comparisons matrix

### 2023-11-06 manuscript/FCPCOM/manuscript.tex
updating files and cleaning

\title{Analytic Hierarchy Process: how to force consistency of pairwise comparisons matrix}

@@

\begin{abstract} 
Saaty's Analytic Hierarchy Process is an important method for assigning weight to multiple criteria. Despite this method represents an important inovation, its logic is not complicated at all. First a pairwise comparisons matrix is generated for the multiple criteria, and the normalized eigenvector of this matrix is used as the weight of criteria. But, since pairwise matrixes are usually generated manually and based only on some employee knowhow, there is a huge complexity on generating a consistent pairwise matrix. Especially when many criteria are used. This paper presents two algorithms that can be used to adjust inconsistent matrices, forcing such matrices to have a better consistency rate. The first method is a constructive method that uses the data inserted in the matrix to build a new improved one. The second method iteratively identifies inconsistencies, making minor changes in order to improve the matrix consistency rate. 
\end{abstract}
%%Graphical abstract
%\begin{graphicalabstract}
%\end{graphicalabstract}

@@

\begin{keyword}
multi-product batch \sep processing time maximization \sep mathematical model \sep analytical solution \sep LINGO
\end{keyword}
\end{frontmatter}

>>>>

\title{ABC multi-criteria classification with analytical hierarchy process: how to force consistency of pairwise comparisons matrix}

@@

\begin{abstract} 
Multicriteria classification is usualy very important to the decision-making in manufacturing management process. For such classification, the attribution of weights to the criteria strongly influences the coherence of the results found. Saaty's Analytic Hierarchy Process (AHP) is an important method for assigning weights to multiple criteria.  AHP's logic is not complicated at all but, since matrices of pairwise comparisons of criteria  are usually generated manually and based only on some employee know-how, there is a huge complexity on generating a consistent pairwise matrix. Especially when many criteria are used. This paper presents a constructive algorithm that can be used to adjust inconsistent matrices, forcing such matrices to have a better consistency rate. We tested this algorithm by applying the AHP method, for ABC multicriteria classification, to companies in two sectors. As a result we observed that the algorithm can adjust the pairwise matrices in just a few seconds, avoiding the manual work that would be done in weeks, therefore showing that it is an important resource for applying the AHP method. 
\end{abstract}
%%Graphical abstract
%\begin{graphicalabstract}
%\end{graphicalabstract}

@@

\begin{keyword}
multi-product batch \sep processing time maximization \sep mathematical model \sep analytical solution \sep COPSolver \sep LINGO
\end{keyword}
\end{frontmatter}
